Barneby Lives usage example

### 2023-05-12 scripts/crop2boundary.Rmd
more abbreviations, fn for naming place

sf::st_read('../geodata/pad/pad.shp', quiet = T) %>% 
  sf::st_make_valid() %>% 
  dplyr::filter(sf::st_is_valid(.)) %>% 
  mutate(Unit_Nm = str_replace(Unit_Nm, "National Forest", "NF"),
         Unit_Nm = str_replace(Unit_Nm, "Field Office", "FO"),
         Unit_Nm = str_replace(Unit_Nm, "National Wildlife Refuge", "NWR")) %>% 
  st_write(., '../geodata/pad/pad.shp', quiet = T, append = F)

@@

>>>>

sf::st_read('../geodata/pad/pad.shp', quiet = T) %>% 
  sf::st_make_valid() %>% 
  dplyr::filter(sf::st_is_valid(.)) %>% 
  mutate(Unit_Nm = str_replace(Unit_Nm, "National Forest", "NF"),
         Unit_Nm = str_replace(Unit_Nm, "District Office", "DO"), 
         Unit_Nm = str_replace(Unit_Nm, "Field Office", "FO"), 
         Unit_Nm = str_replace(Unit_Nm, "National Park", "NP"),
         Unit_Nm = str_replace(Unit_Nm, 'National Grassland', 'NG'),
         Unit_Nm = str_replace(Unit_Nm, "National Wildlife Refuge|National Wildlife Range", "NWR"),
         Unit_Nm = str_replace(Unit_Nm, 'National Monument', 'NM'),
         Unit_Nm = str_replace(Unit_Nm, "National Recreation Area", "NRA"), 
         Unit_Nm = str_replace(Unit_Nm, "State Resource Management Area", "SRMA"), 
         Unit_Nm = str_replace(Unit_Nm, "State Trust Lands", "STL"), 
         Unit_Nm = str_replace(Unit_Nm, "Department", "Dept."),
         Unit_Nm = str_replace(Unit_Nm, "Recreation Area", "Rec. Area"),
         Unit_Nm = str_replace(Unit_Nm, 'Wildlife Habitat Management Area', "WHMA"), 
         Unit_Nm = str_replace(Unit_Nm, 'Wildlife Management Area', "WMA")) %>% 
  st_write(., '../geodata/pad/pad.shp', quiet = T, append = F)

sf::st_read('../geodata/places/places.shp', quiet = T) %>% 
  mutate(
    fetr_nm = str_remove(fetr_nm, ' Census Designated Place' ),
    fetr_nm = str_remove(fetr_nm, 'Township of '), 
    fetr_nm = str_remove(fetr_nm, ' \\(historical\\)'),
    fetr_nm = str_remove(fetr_nm, 'Village of '),
    fetr_nm = str_remove(fetr_nm, 'Town of '), 
    fetr_nm = str_remove(fetr_nm, 'City of ')
    ) %>% 
  filter(!str_detect(fetr_nm,
                     'Election Precinct| County|Ditch|Unorganized Territory|Canal|Lateral|Division|
                     River Division|Drain Number|Waste Pond|Commissioner District|Lake Superior|Lake Michigan')) %>% 
  mutate(
    fetr_nm = str_replace(fetr_nm, ' Canyon', ' cnyn.'),
    fetr_nm = str_replace(fetr_nm, ' Campground', ' cmpgrnd.'),
    fetr_nm = str_replace(fetr_nm, ' Creek', ' crk.'),
    fetr_nm = str_replace(fetr_nm, ' Fork', ' fk.'),
    fetr_nm = str_replace(fetr_nm, ' Lake', ' lk.'),
    fetr_nm = str_replace(fetr_nm, ' Meadows', ' mdws.'),
    fetr_nm = str_replace(fetr_nm, ' Meadow', ' mdw.'),
    fetr_nm = str_replace(fetr_nm, ' Mountains', ' mtns.'),
    fetr_nm = str_replace(fetr_nm, ' Mountain', ' mtn.'),
    fetr_nm = str_replace(fetr_nm, ' Number', ' #'),
    fetr_nm = str_replace(fetr_nm, ' Point', ' pt.'),
    fetr_nm = str_replace(fetr_nm, ' Reservoir', ' rsvr.'),
    fetr_nm = str_replace(fetr_nm, ' River ', ' rvr.')
  ) %>% 
  st_write(., '../geodata/places/places.shp', quiet = T, append = F)

@@

' Point', ' pt.'

### 2023-05-12 scripts/project_template.Rmd
more abbreviations, fn for naming place

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 500), seq(1:500)),
  day = c(sample(1:31, size = 500, replace = T)),
  month = c(sample(5:10, size = 500, replace = T)),
  year = 2023,
  x = runif(500, min = -120, max = -85), 
  y = runif(500, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

# if within 0.5 km of place, use
# if dist > 0.5 km direct

>>>>

```{r}
library(tidyverse)
library(sf)
source('functions.R')
```

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 500), seq(1:500)),
  day = c(sample(1:31, size = 500, replace = T)),
  month = c(sample(5:10, size = 500, replace = T)),
  year = 2023,
  x = runif(500, min = -120, max = -100), 
  y = runif(500, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

rm(out)
# if within 0.5 km of place, use
# if dist > 0.5 km direct
